UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-11 files/paper/paper.tex
update

Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This is due
to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually, which batch
normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer},
but we found no significant improvements. RESULTS PENDING
In all of our experiments, we use $\lambda_{L1} = 100$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$. Our implementation was done
using the Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}

\section{Experiments}

Here I want to show a number of things. First talk about the datasets used, Imagenet and the diving videos.
Second, show some general results. Explain how our network is able to do three very important things: 1) Restore an
image to its natural colors with varying amounts of distortion, i.e. blue hue, green hue, aka not just one type of
color distortion. 2) The network does not just subtract a certain hue from the entire image. Show how in the clownfish
image, part of the image has good colors, while part of it doesn't. Our network is able to leave correct colors. Third,
show that even images taken towards the water's surface, either above or below, are able to be restored correctly.

@@

>>>>

Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This
is due to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually,
which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{L1} = 100$,
batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$. Our
implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}

\section{Experiments}
\subsection{Datasets}
We used several subsets of Imagenet \cite{deng2009imagenet} for training and evaluation of our methods. We also
evaluate a tracking algorithm on a diving video taken from Youtube. Subsets of Imagenet containing underwater images
were selected for the training of CycleGAN, and manually separated into two classes. We let $X$ be the set of
underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$ contained 6143
images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that
images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
all images in $X$ with $F$. Figure 2 shows sample training pairs.

\subsection{Evaluation}
We trained UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluated on the images from the test set, $Y$.
Note that these images do not contain any ground truth, as they are original distorted images from Imagenet. Images for
training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.

\subsection{Comparison to CycleGAN}

It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance.
Here I want to show a number of things. First talk about the datasets used, Imagenet and the diving videos.
Second, show some general results. Explain how our network is able to do three very important things: 1) Restore an
image to its natural colors with varying amounts of distortion, i.e. blue hue, green hue, aka not just one type of
color distortion. 2) The network does not just subtract a certain hue from the entire image. Show how in the clownfish
image, part of the image has good colors, while part of it doesn't. Our network is able to leave correct colors. Third,
show that even images taken towards the water's surface, either above or below, are able to be restored correctly.

@@

\subsection{Diver Tracking}
